---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# flatforwardCOPOM

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/flatforwardCOPOM)](https://CRAN.R-project.org/package=flatforwardCOPOM)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of flatforwardCOPOM is to interpolate term structures of interest rates taking into account the meetings where the regulators discuss
the changes on interest rates.

In Brazil these meetins are called COPOM and this interpolation considers
that the interest rate between COPOM meetings are flat, instead of being
flat betweet bonds maturities.

This is mainly  for the short term of the term structure where
the interpolation is used to price private bonds and interest rate
derivatives.

## Installation

You can install the development version of flatforwardCOPOM from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("wilsonfreitas/flatforwardCOPOM")
```

## Example

```{r example}
library(bizdays)
library(fixedincome)
library(flatforwardCOPOM)

copom_dates <- as.Date(
  c("2022-03-17", "2022-05-05", "2022-06-17", "2022-08-04")
)
terms <- c(1, 3, 25, 44, 66, 87, 108, 131, 152, 172, 192, 214, 236, 277)
rates <- c(
  0.1065, 0.1064, 0.111, 0.1138, 0.1168, 0.1189, 0.1207, 0.1219,
  0.1227, 0.1235, 0.1234, 0.1236, 0.1235, 0.1235
)
curve <- spotratecurve(
  rates, terms, "discrete", "business/252", "Brazil/ANBIMA",
  refdate = as.Date("2022-02-23")
)
interpolation(curve) <- interp_flatforwardcopom(copom_dates, "second")

plot(curve, use_interpolation = TRUE, show_forward = TRUE,
     legend_location = "bottomright")
```
