---
title: "Introduction to copom package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{copom-intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## copom

Start attaching `copom`.

```{r message=FALSE, warning=FALSE}
library(copom)
```

It attachs `bizdays` and `fixedincome`.

## Create a curve

Let's create by hand the curve to be used in this tutorial.
You must provide the curve terms and corresponding rates.
The terms must be provided according to `daycount` used.

```{r curve}
terms <- c(1, 3, 25, 44, 66, 87, 108, 131, 152, 172, 192, 214, 236, 277)
rates <- c(
  0.1065, 0.1064, 0.111, 0.1138, 0.1168, 0.1189, 0.1207, 0.1219,
  0.1227, 0.1235, 0.1234, 0.1236, 0.1235, 0.1235
)
curve <- spotratecurve(
  rates, terms, "discrete", "business/252", "Brazil/ANBIMA",
  refdate = as.Date("2022-02-23")
)
```

Here we use the daycount `business/252`, so the terms are business days.

## Create the copom interpolation

Now we have a curve, we define the interpolation method by creating an
`Interpolation` object with the function `interp_flatforwardcopom`.
We pass a vector with the dates of the meetings
to be used in the interpolation and set `conflicts = "second"`.
There are periods between meetings that have two points and, in this cases,
the second point will be used in the interpolation.

Once the Interpolation object is created, it is set to the curve with
the `interpolation<-` method.

```{r}
copom_dates <- as.Date(
  c("2022-03-17", "2022-05-05", "2022-06-17", "2022-08-04")
)
interpolation(curve) <- interp_flatforwardcopom(copom_dates, "second")
```

## Visualize the interpolation

With everything set the curve can be easily viewed with `plot`.

```{r plot}
plot(curve,
  use_interpolation = TRUE, show_forward = TRUE,
  legend_location = "bottomright"
)
```

To compare with the flat forward interpolation let's visualize the curve with 
this different intepolation.

```{r}
interpolation(curve) <- interp_flatforward()
plot(curve,
  use_interpolation = TRUE, show_forward = TRUE,
  legend_location = "bottomright"
)
```

In the long term there isn't mush difference, but in the short term the
interpolated points and the forward rates are fairly different.
