---
title: "Introduction to flatforwardCOPOM"
author: "Wilson Freitas"
date: "12/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## flatforwardCOPOM

Start attaching the packages `bizdays`, `fixedincome` and `flatforwardCOPOM`.
The `bizdays` package must be loaded because the calendar `Brazil/ANBIMA` is
refferenced and it is attached together with `bizdays`.
Otherwise the used calendars should be created first.


```{r message=FALSE, warning=FALSE}
library(bizdays)
library(fixedincome)
library(flatforwardCOPOM)
```

## Create a curve

Let's create by hand the curve to be used in this tutorial.

```{r curve}
terms <- c(1, 3, 25, 44, 66, 87, 108, 131, 152, 172, 192, 214, 236, 277)
rates <- c(
  0.1065, 0.1064, 0.111, 0.1138, 0.1168, 0.1189, 0.1207, 0.1219,
  0.1227, 0.1235, 0.1234, 0.1236, 0.1235, 0.1235
)
curve <- spotratecurve(
  rates, terms, "discrete", "business/252", "Brazil/ANBIMA",
  refdate = as.Date("2022-02-23")
)
```

## Create the FlatForwardCOPOM interpolation

Call `interp_flatforwardcopom` passing a vector with the dates of the meetings
to be used in the interpolation.
The `conflicts = "second"` will be used, since there are periods between
meetings that have two points.
In this cases, the second point will be used in the interpolation.

Once the Interpolation object is create, it is set to the curve with
`interpolation<-` method.

```{r}
copom_dates <- as.Date(
  c("2022-03-17", "2022-05-05", "2022-06-17", "2022-08-04")
)
interpolation(curve) <- interp_flatforwardcopom(copom_dates, "second")
```

## Visualize the interpolation

With everything set the curve can be easily viewed with `plot`.

```{r plot}
plot(curve, use_interpolation = TRUE, show_forward = TRUE,
     legend_location = "bottomright")
```

To compare with the flat forward interpolation let's visualize the curve with 
this different intepolation.

```{r}
interpolation(curve) <- interp_flatforward()
plot(curve, use_interpolation = TRUE, show_forward = TRUE,
     legend_location = "bottomright")
```

In the long term there isn't mush difference, but in the short term the
interpolated points and the forward rates are fairly different.
